Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2019-05-06 doc/network.tex
update

\swp{What do I cite here? Gillespie?}
We use individual-based simulations of the stochastic SEIR model on a network to study variation in realized generation intervals.
Every node of a network is numbered from 1 to $N$, where $N$ is the total number of nodes. 
Each node represents an individual.
Likewise, an edge of a network represents acquaintanceship; infected individuals can only contact their acquaintances.

First, we begin by randomly selecting initially infected individuals.
For each infected individual $i$, we randomly draw a random number $E_i$ from an Erlang distribution with mean $1/\sigma$ and shape $n_E$.
Given a total contact rate of $k_i \lambda$, where $k_i$ is the number of acquaintances and $\lambda$ is the per-pair contact rate, and a transition rate of $n_I \gamma$ between each infectious stages, 
the total number of contacts that an indiviudal $i$ in infectious stage $j$ makes before moving to infectious stage $j+1$ follows a geometric distribution with probability $n_I\gamma/(k_i \lambda + n_I\gamma)$:
\begin{equation}
C_{i, j} \sim \mathrm{Geometric}\left(\frac{n_I\gamma}{k_i \lambda + n_I\gamma}\right).
\end{equation}
For each contact, a contactee is uniformly sampled from the set of acquaintances of the individual $i$.

>>>>

\swp{What do I cite here?}
We develop an algorithm to simulate an individual-based SEIR model on a network to keep track of generation intervals.
Our algorithm is based on the Gillespie algorithm.
We model individuals with nodes on a network and their acquaintanceships with edges; infected individuals can only contact their acquaintances.

First, we begin by randomly selecting initially infected individuals; these individuals are assumed to be infected at $t = 0$.
For each infected individual $i$, we randomly draw a random number $E_i$ from an Erlang distribution with mean $1/\sigma$ and shape $n_E$ to represent the length of their latent period.
Given a total contact rate of $S_i \lambda$, where $S_i$ is the number of susceptible acquaintances and $\lambda$ is the per-pair contact rate, and a transition rate of $n_I \gamma$ between each infectious stages, 
the total number of contacts that an indiviudal $i$ in infectious stage $j$ makes before moving to infectious stage $j+1$ follows a geometric distribution with probability $n_I\gamma/(S_i \lambda + n_I\gamma)$:
\begin{equation}
C_{i, j} \sim \mathrm{Geometric}\left(\frac{n_I\gamma}{S_i \lambda + n_I\gamma}\right).
\end{equation}
For each contact, a contactee is uniformly sampled from the set of acquaintances of the individual $i$.
Then, the time between two events follows an exponential distribution with rate $S_i \lambda + n_I\gamma$:
\begin{equation}
T_{i, j, k} \sim \mathrm{Exponential}\left(S_i \lambda + n_I\gamma\right),
\end{equation}
where $k = 1, 2, \dots, C_{i, j}, C_{i, j} + 1$. Here, the $(C_{i, j} + 1)$-th event is the transition from the infectious stage from $j$ to $j+1$.
This process is repeated until the individual fully recovers (i.e., goes through all infectious stages).
Then, the time at which individual $i$ makes $k$-th contact is given by the sum of current time $t$, the length of latent period $E_i$, and the time between all events (either a contact or transistion between states) caused by this individual prior to the contact:
\begin{equation}
\begin{cases}
t + E_i + \sum_{n=1}^k T_{i, j, n}, & \text{if } j = 1,\\
t + E_i + \sum_{m=1}^{j-1} \sum_{n=1}^{C_{i, m} + 1} T_{i, m, n} + \sum_{n=1}^k T_{i, j, n}, & \text{if } j > 1,
\end{cases}
\end{equation}
